Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-02 manuscript/manuscript.Rmd
update tables

|variable       |label                                       | relativity|
|:--------------|:-------------------------------------------|----------:|
|occupancy_type |Single family residence                     |       1.00|
|occupancy_type |Non-residential building                    |       1.37|
|occupancy_type |2 to 4 unit residential buidling            |       1.15|
|occupancy_type |Residential building with more than 4 units |       1.64|
|flood_zone     |B                                           |       1.00|
|flood_zone     |A                                           |       0.84|
|flood_zone     |C                                           |       0.60|
|flood_zone     |X                                           |       0.70|
|flood_zone     |V                                           |       0.78|
|flood_zone     |D                                           |       0.89|

@@

|level                                       | embedding|
|:-------------------------------------------|---------:|
|2 to 4 unit residential buidling            |      6.69|
|Non-residential building                    |      7.16|
|Residential building with more than 4 units |      6.33|
|Single family residence                     |      5.43|

@@

|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
|A     |      0.38|A09   |     -1.71|A18   |     -1.40|A99   |     -2.68|V     |     -0.41|
|A00   |     -0.35|A0B   |      3.85|A19   |     -1.70|AE    |     -4.46|V02   |      0.65|
|A01   |     -6.76|A10   |     -4.03|A20   |     -4.05|AH    |     -2.35|V03   |     -0.29|
|A02   |     -4.28|A11   |     -5.32|A21   |     -2.08|AHB   |     -1.71|V04   |     -1.15|
|A03   |     -5.93|A12   |     -3.23|A22   |     -2.11|AO    |     -6.07|V05   |     -0.50|
|A04   |     -7.82|A13   |      2.03|A23   |     -1.40|AOB   |     -4.56|V06   |     -1.92|
|A05   |     -3.42|A14   |     -5.72|A24   |      2.23|AR    |     -0.48|V07   |     -2.91|
|A06   |     -4.97|A15   |     -3.67|A25   |      0.28|B     |     -5.36|V08   |     -2.24|
|A07   |     -3.09|A16   |     -3.02|A27   |     -2.56|C     |     -4.47|V09   |     -0.75|
|A08   |     -4.69|A17   |     -0.37|A30   |      1.13|D     |     -0.76|V10   |     -2.05|

@@

|term                                     | estimate|
|:----------------------------------------|--------:|
|(Intercept)                              |    2.389|
|total_building_insurance_coverage        |    0.568|
|basement_enclosure_crawlspace_type       |    0.136|
|number_of_floors_in_the_insured_building |   -0.024|
|occupancy_type                           |    0.067|
|flood_zone                               |    0.035|
|primary_residence                        |   -0.001|
|community_rating_system_discount         |    0.504|

@@

|level                                       |    e1|    e2|   e3|
|:-------------------------------------------|-----:|-----:|----:|
|2 to 4 unit residential buidling            | -1.44| -1.97| 2.35|
|Non-residential building                    | -6.83| -8.11| 5.34|
|Residential building with more than 4 units | -7.63| -6.58| 5.09|
|Single family residence                     | -1.61| -2.54| 3.01|

@@

|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
|e1        |0.020  |e11       |2.146  |e21       |-1.933 |e31       |-0.941 |
|e2        |-0.885 |e12       |1.723  |e22       |1.150  |e32       |-1.279 |
|e3        |-0.126 |e13       |0.378  |e23       |0.863  |e33       |-0.360 |
|e4        |1.491  |e14       |-0.310 |e24       |-0.471 |e34       |-1.173 |
|e5        |0.980  |e15       |2.482  |e25       |0.929  |          |       |
|e6        |0.952  |e16       |1.823  |e26       |-1.139 |          |       |
|e7        |-0.217 |e17       |-2.715 |e27       |0.113  |          |       |
|e8        |-0.611 |e18       |1.144  |e28       |1.155  |          |       |
|e9        |0.919  |e19       |-0.045 |e29       |0.707  |          |       |
|e10       |-1.196 |e20       |0.467  |e30       |1.358  |          |       |

>>>>

|variable       |label                                       | relativity|
|:--------------|:-------------------------------------------|----------:|
|occupancy_type |Single family residence                     |       1.00|
|occupancy_type |2 to 4 unit residential buidling            |       1.10|
|occupancy_type |Non-residential building                    |       1.34|
|occupancy_type |Residential building with more than 4 units |       1.59|
|flood_zone     |C                                           |       1.00|
|flood_zone     |A                                           |       1.42|
|flood_zone     |X                                           |       1.18|
|flood_zone     |B                                           |       1.65|
|flood_zone     |V                                           |       1.38|
|flood_zone     |D                                           |       1.45|

@@

|level                                       | embedding|
|:-------------------------------------------|---------:|
|2 to 4 unit residential buidling            |      1.46|
|Non-residential building                    |     -1.04|
|Residential building with more than 4 units |      0.12|
|Single family residence                     |      0.36|

@@

|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
|A     |      1.48|A09   |     -0.48|A18   |      0.39|A28   |      1.19|C     |      1.73|
|A00   |     -1.05|A0B   |      1.47|A19   |     -1.06|A30   |     -0.01|D     |     -1.15|
|A01   |     -0.18|A10   |     -0.25|A20   |     -1.01|A99   |     -0.44|V     |     -1.85|
|A02   |     -0.06|A11   |      0.35|A21   |      2.08|AE    |      1.12|V01   |      0.02|
|A03   |     -0.01|A12   |     -0.38|A22   |     -0.15|AH    |      2.19|V02   |     -1.55|
|A04   |      0.05|A13   |      2.81|A23   |     -0.76|AHB   |     -0.68|V03   |     -0.98|
|A05   |      1.30|A14   |      0.58|A24   |     -0.87|AO    |      0.55|V04   |      1.73|
|A06   |     -0.76|A15   |     -0.91|A25   |      0.02|AOB   |      0.08|V05   |     -1.97|
|A07   |     -0.62|A16   |      0.79|A26   |      0.00|AR    |      2.93|V06   |      0.43|
|A08   |     -0.53|A17   |      1.35|A27   |      0.80|B     |      0.33|V07   |      1.91||

@@

|term                                     | estimate|
|:----------------------------------------|--------:|
|(Intercept)                              |    3.371|
|total_building_insurance_coverage        |    0.586|
|basement_enclosure_crawlspace_type       |    0.597|
|number_of_floors_in_the_insured_building |   -0.278|
|occupancy_type                           |   -0.075|
|flood_zone                               |   -0.007|
|primary_residence                        |   -0.062|
|community_rating_system_discount         |    0.706|

@@

|level                                       |    e1|    e2|    e3|
|:-------------------------------------------|-----:|-----:|-----:|
|2 to 4 unit residential buidling            |  0.37| -1.76|  1.36|
|Non-residential building                    |  0.13|  1.47|  1.77|
|Residential building with more than 4 units | -1.12| -0.15| -1.43|
|Single family residence                     |  0.85|  0.16| -0.99|

@@

|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
|e1        |-0.167 |e11       |-0.810 |e21       |-0.300 |e31       |-0.421 |
|e2        |-0.363 |e12       |1.380  |e22       |-0.194 |e32       |0.594  |
|e3        |-0.893 |e13       |-0.180 |e23       |-0.320 |e33       |1.681  |
|e4        |0.130  |e14       |-1.612 |e24       |-0.035 |e34       |1.668  |
|e5        |-1.588 |e15       |-1.327 |e25       |-1.128 |          |       |
|e6        |-0.123 |e16       |-0.965 |e26       |0.168  |          |       |
|e7        |-0.259 |e17       |-1.356 |e27       |-1.022 |          |       |
|e8        |0.324  |e18       |-0.061 |e28       |1.011  |          |       |
|e9        |-1.430 |e19       |-0.120 |e29       |-0.843 |          |       |
|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       ||
